---
title: "SP-tutorials" 
author: "Author: Daniela Cassol (danielac@ucr.edu)"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`" 
output:
  BiocStyle::html_document:
    toc_float: true
    code_folding: show
package: systemPipeR
vignette: |
  %\VignetteEncoding{UTF-8}
  %\VignetteIndexEntry{SP-tutorials}
  %\VignetteEngine{knitr::rmarkdown}
fontsize: 14pt
bibliography: bibtex.bib
---

# Integration with Jupter notebooks

_systemPipeR_ [@H_Backman2016-bt] relies on `RMarkdown` or `.R` format to organize 
the code and execute the commands. However, if your code is in a Jupyter/IPython 
notebook file (`.ipynb` format), it is possible to convert its code cells to RMarkdown
code chunks, as follow:

```{r}
rmarkdown:::convert_ipynb("notebook.ipynb", output = xfun::with_ext("notebook.ipynb", "Rmd"))
```

or from Bash:

```{bash, eval=FALSE}
jupytext notebook.ipynb --output notebook.Rmd
## OR
jupytext notebook.ipynb --output notebook.R
```

To convert from `.Rmd` to `.ipynb` format, use:

```{bash, eval=FALSE}
jupytext --to notebook notebook.Rmd 
```

# Version Information

```{r sessionInfo}
sessionInfo()
```

# References
 